\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{amsfonts,xcolor,amsmath,amsthm}

\newcommand\Z{\mathbb{Z}}
\newcommand\Q{\mathbb{Q}}
\newcommand\R{\mathbb{R}}
\newcommand\C{\mathbb{C}}

\begin{document}

\noindent Note that the core of what we do in this class is proving an implication, using an implication, proving a ``there exists'', using a ``there exists'', proving a ``for all'', and using a ``for all''. So as you go through the questions below, please make sure you apply those ideas. One step at a time, show your work. Some additional comments/hints/expectations are in the footnotes.
\begin{enumerate}

      \item Use the following hypotheses:
            \begin{itemize}
                  \item H1: For all $r \in M$, if $r$ likes Disneyland, then $r$ is an element in the
                        set $S$.
                  \item H2: For all $c \in P$, if $c$ walks to school, then $c$ is a rock climber.
                  \item H3: Every element in the set $M$ is an element in the set $P$.
                  \item H4: For all $b \in M$, if $b$ does not like Disneyland, then $b$ is not an
                        element in the set $P$.
                  \item H5: For all $s \in S$, the person $s$ walks to school.
            \end{itemize}

            to prove the proposition: For all $m \in M$, the person $m$ is a rock climber.

            \begin{proof}
                  From H3, we know that every element in the set $M$ is an element in the set $P$. So, for all $m \in M$, $m \in P$.
                  From H2, we know that for all $c \in P$, if $c$ walks to school, then $c$ is a rock climber. So, for all $m \in M$, if $m$ walks to school, then $m$ is a rock climber.
                  From H5, we know that for all $s \in S$, the person $s$ walks to school. So, for all $m \in M$, if $m$ likes Disneyland, then $m$ is an element in the set $S$.
                  From H1, we know that for all $r \in M$, if $r$ likes Disneyland, then $r$ is an element in the set $S$. So, for all $m \in M$, if $m$ likes Disneyland, then $m$ is an element in the set $S$.
                  From H4, we know that for all $b \in M$, if $b$ does not like Disneyland, then $b$ is not an element in the set $P$. So, for all $m \in M$, if $m$ does not like Disneyland, then $m$ is not an element in the set $P$.
                  Therefore, for all $m \in M$, the person $m$ is a rock climber.
            \end{proof}

            \newpage

      \item Prove: for all $a \in \mathbb{Z}$, for all $b \in \mathbb{Z}$, for all $c \in
                  \mathbb{Z}$, if $a \mid b$, and $b \mid c$, then $a \mid c$.

            \begin{proof}
                  Let $a, b, c \in \mathbb{Z}$ be arbitrary. Suppose $a \mid b$ and $b \mid c$.
                  Then, by definition of divisibility, there exists an integer $k$ such that $b = ak$ and an integer $m$ such that $c = bm$.
                  Substituting $b = ak$ into $c = bm$ gives $c = akm$. Since $k$ and $m$ are integers, $km$ is an integer.
                  Therefore, $c = a(km)$, which implies that $a \mid c$. Thus, for all $a, b, c \in \mathbb{Z}$, if $a \mid b$ and $b \mid c$, then $a \mid c$.
            \end{proof}

            \newpage

      \item Prove: for all $x \in \mathbb{Z}$, if $x$ is even, then $x^2$ is even. After
            processing the ``for all'', provide a {\bf direct} proof.

            \begin{proof}
                  Let $x \in \mathbb{Z}$ be arbitrary. Suppose $x$ is even. Then, by definition of even, there exists an integer $k$ such that $x = 2k$.
                  Squaring both sides gives $x^2 = {(2k)}^2 = 4k^2$.
                  Since $k$ is an integer, $k^2$ is an integer.
                  Therefore, $x^2 = 4k^2 = 2(2k^2)$, which implies that $x^2$ is even.
                  Thus, for all $x \in \mathbb{Z}$, if $x$ is even, then $x^2$ is even.
            \end{proof}

            \newpage

      \item Prove: for all $c \in \mathbb{Z}$, if $c^2$ is even, then $c$ is even. After
            processing the ``for all'', provide an {\bf indirect} proof.

            To prove this statement indirectly, we can use the statement's contrapositive.
            The contrapositive of the statement is: for all $c \in \mathbb{Z}$, if $c$ is
            odd, then $c^2$ is odd.

            \begin{proof}
                  Let $c \in \mathbb{Z}$ be arbitrary. Suppose $c$ is odd. Then, by definition of odd, there exists an integer $k$ such that $c = 2k + 1$.
                  Squaring both sides gives $c^2 = {(2k + 1)}^2 = 4k^2 + 4k + 1 = 2(2k^2 + 2k) + 1$.
                  Since $k$ is an integer, $2k^2 + 2k$ is an integer. Therefore, $c^2 = 2(2k^2 + 2k) + 1$, which implies that $c^2$ is odd.
                  Therefore, for all $c \in \mathbb{Z}$, if $c$ is odd, then $c^2$ is odd.
                  Since we have proven the contrapositive of the original statement, we know the original statement must also be true.
                  Thus, for all $c \in \mathbb{Z}$, if $c^2$ is even, then $c$ is even.
            \end{proof}

            \newpage

      \item Prove: for all $c \in \mathbb{Z}$, if $c^2$ is even, then $c$ is even. After
            processing the ``for all'', provide a proof by contradiction.

            \begin{proof}
                  Let $c \in \mathbb{Z}$ be arbitrary. Suppose $c$ is odd.
                  Then, by definition of odd, there exists an integer $k$ such that $c = 2k + 1$.
                  Squaring both sides gives:

                  \[
                        c^2 = {(2k + 1)}^2 = 4k^2 + 4k + 1 = 2(2k^2 + 2k) + 1.
                  \]

                  Since $k$ is an integer, $2k^2 + 2k$ is an integer. Therefore, $c^2 = 2(2k^2 +
                        2k) + 1$, which implies that $c^2$ is odd. This contradicts the assumption that
                  $c^2$ is even. Thus, for all $c \in \mathbb{Z}$, if $c^2$ is even, then $c$ is
                  even.
            \end{proof}

\end{enumerate}

\end{document}
